Method to infer relatedness using low coverage ancient DNA

### 2021-12-23 paper_overleaf/main.tex

- lcMLKIn and kin ibd
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/lcPlot.png}
    \caption{Application of lcMLkin on Neandertal specimens from Chagyrskaya.}
    \label{figS3}
\end{figure}

-2nd degree with 10M windows
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/degree2_10Mwin.png}
    \caption{2deg}
    \label{figS4}
\end{figure}

>>>>

-effect of bounding variance on emission. Here is an identical pair, with identical model transitions with and without variance constraints
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_emissions_bnds.png}
    \caption{Emission with bnds}
    \label{figS3}
\end{figure}

-effect of bounding variance on beta. Here is an identical pair, with identical model transitions with and without emissions
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_relid_betaplot.png}
    \caption{beta with bnds}
    \label{figS3}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/contam0_inbred1_run57_coverage0.2_asc0_inputMode_hapProbs_fil0_pair0_15_reli
    \caption{beta with bnds}
    \label{figS3}
\end{figure}

- lcMLKIn and kin ibd
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/lcPlot.png}
    \caption{Application of lcMLkin on Neandertal specimens from Chagyrskaya.}
    \label{figS4}
\end{figure}

-2nd degree with 10M windows
\begin{figure}[htp]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/degree2_10Mwin.png}
    \caption{2deg}
    \label{figS5}
\end{figure}
